A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

In Section~\ref{section:pca_linreg}, fundamental mathematics of SVD and associated properties are presented. Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work. Finally, Section~\ref{section:pca_linreg} describes the reduced order model reduction for the permeability field within the principal component space. Section~\ref{section:model_simulation} is dedicated to model description and simulation. It starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to. A brief summary of the pre-processing step for each of the models is also presented. Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique. Finally, Conclusions are drawn in Section~\ref{section:conclusion}.

>>>>

In Section~\ref{section:pca_linreg}, fundamental mathematics of SVD and associated properties are presented. Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work. Finally, Section~\ref{section:pca_linreg} describes the reduced order model reduction for the permeability field within the principal component space. Section~\ref{section:model_simulation} is dedicated to model description and simulation. It starts by describing the high-resolution problem (\ie `base case') in which the four upscaling techniques are applied to. A brief summary of the pre-processing steps for each of the models is also presented. Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique. Finally, Conclusions are drawn in Section~\ref{section:conclusion}.
